---
title: "REVIEW: Analysis of the MRIO embodied landscape literature"
author: MK Lau
date: 
output: md_document
fig_caption: yes
bibliography: refs.bib
always_allow_html: yes

# Latex settings
header-includes:
  - \usepackage{endfloat}
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=600)
```


- Resilience metrics for networks of embodied landscapes
  - Landscape context
  - Disturbances
  - Conversion
- What is resilience?
  - Ecology and resilience
  - Complex systems resilience
	- MacArthur
	- May
	- Ulanowicz
	- Sheffer
- Environmental embodied trade networks
  - IO background
  - Environmental/Social
  - Landscapes
- Network metrics and resilience
  - FATH
  - Bascompte
  - Ulanowicz
- Review methods and overview
- Review: Metrics
  - IO -> MRIO -> EEMRIO
  - LEMRIO
  - IO overlap with ENA
  - ENA(IO) + ENA(LEMRIO)
- Needs and Directions
  - Climate change
  - Disturbance

# Analyses

- What work has been done on landscape mrio?
- What work has addressed resilience and stability?
- What ENA metrics have been or could be applied?

```{r loadd-data, echo=TRUE, message=FALSE, warning=FALSE}

loadd(io.bdf)

```

## keyword+title: mrio & landscape

```{r mrio-land, echo=TRUE, message=FALSE, warning=FALSE}

q.ml <- grepl("^LAND", io.bdf[, "DE"]) | 
    grepl("^LAND", io.bdf[, "TI"]) | 
    grepl(" LAND", io.bdf[, "DE"]) | 
    grepl(" LAND", io.bdf[, "TI"]) 

```

## keyword+title: mrio & network/ena

```{r mrio-ena, echo=TRUE, message=FALSE, warning=FALSE}

q.net <- (grepl("NETWORK ANALYS", io.bdf[, "DE"]) | 
    grepl("NETWORK ANALYS", io.bdf[, "TI"])) & 
	!(grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "DE"]) | 
    grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "TI"]))
q.me <- grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "DE"]) | 
    grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "TI"]) &
    !(q.net)

```

## keyword+title: resilience

```{r mrio-res, echo=TRUE, message=FALSE, warning=FALSE}

q.res <- grepl("^RESILIEN", io.bdf[, "TI"]) | 
    grepl("^RESILIEN", io.bdf[, "DE"]) | 
    grepl(" RESILIEN", io.bdf[, "TI"]) | 
    grepl(" RESILIEN", io.bdf[, "DE"]) 
q.res.abs <- grepl("^RESILIEN", io.bdf[, "TI"]) | 
    grepl("^RESILIEN", io.bdf[, "DE"]) | 
    grepl(" RESILIEN", io.bdf[, "TI"]) | 
    grepl(" RESILIEN", io.bdf[, "DE"]) | 
    grepl("^RESILIEN", io.bdf[, "AB"]) | 
    grepl(" RESILIEN", io.bdf[, "AB"]) 

```

## keyword+title: disturbance(climate change, other)

```{r mrio-dist, echo=TRUE, message=FALSE, warning=FALSE}

q.mc <- grepl("^CLIMATE", io.bdf[, "TI"]) | 
    grepl("^CLIMATE", io.bdf[, "DE"]) | 
    grepl(" CLIMATE", io.bdf[, "TI"]) | 
    grepl(" CLIMATE", io.bdf[, "DE"]) 

q.md <- grepl("^DISTURB", io.bdf[, "TI"]) | 
    grepl("^DISTURB", io.bdf[, "DE"]) | 
    grepl(" DISTURB", io.bdf[, "TI"]) | 
    grepl(" DISTURB", io.bdf[, "DE"]) 

```

## keyword+title: coupled-human natural systems

```{r mrio-chns, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.res.abs & q.ml, "AB"]

```
## keyword+title: ena & resilience+stability & metrics

```{r mrio-met, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.res.abs & q.ml, "AB"]

```
## type: review 

```{r mrio-rev, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.res.abs & q.ml, "AB"]

```





```{r figRef, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure caption here"}
plot(1:5)

```

\@ref(fig:figRef) 


```{r tabRef, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
# data(iris)
# df <- head(iris)
# knitr::kable(df, caption = "Table caption here...", booktabs = TRUE)
```

\@ref(tab:tabRef)


# References
