---
title: "REVIEW: Analysis of the MRIO embodied landscape literature"
author: MK Lau
date: 
output: md_document
fig_caption: yes
bibliography: refs.bib
always_allow_html: yes

# Latex settings
header-includes:
  - \usepackage{endfloat}
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=600)
```

# Overview

Summary: The goal of this review is to identify the needs for network
analysis of landscape (forests, agriculture, aquatic, built) embodied
in trade to assess the resilience of global human-natural systems to
climate change.

- Why landscape?
  - Major topics in landscape
	- Land-use change
	- Climate change
	- Invasive/disease organisms
	- Fire and drought
   - Resilience and sustainability
- Why MRIO?
  - Multi-regional
  - Multi-industry
- Why networks, why ENA?
  - System-wide impacts through both direct and indirect pathways
  - Feedbacks and cycling
  - Groups and modules
  - ENA is based on IO Analysis framework
  - Compare Approaches (network vs non-network)
	- ENA
	- IO analysis
	- Telecoupling
	- Footprint analysis
	- Other? See Ecol. Econ. 2015 114
	- Virtual systems?
- What has been done?
- What are the priorities?
  - Climate change
  - Land-use change
  - Structural analyses
	- Targets
	- Metrics
  - Coupled Industries
- Comparison of network and non-network metrics


# Analyses

- What work has been done on landscape mrio?
- What work has addressed resilience and stability?
- What ENA metrics have been or could be applied?

```{r loadd-data, echo=TRUE, message=FALSE, warning=FALSE}

loadd(io.bdf)

```


## keyword+title: io/mrio

```{r mrio-io, echo=TRUE, message=FALSE, warning=FALSE}

q.mrio <- grepl("INPUT-OUTPUT", io.bdf[, "DE"]) | 
    grepl("INPUT-OUTPUT", io.bdf[, "TI"]) | 
    grepl("INPUT OUTPUT", io.bdf[, "DE"]) | 
    grepl("INPUT OUTPUT", io.bdf[, "TI"]) 

```

## keyword+title: mrio & landscape

```{r mrio-land, echo=TRUE, message=FALSE, warning=FALSE}

q.land <- grepl("^LAND", io.bdf[, "DE"]) | 
    grepl("^LAND", io.bdf[, "TI"]) | 
    grepl(" LAND", io.bdf[, "DE"]) | 
    grepl(" LAND", io.bdf[, "TI"]) 

```

## keyword+title: mrio & network/ena

```{r mrio-ena, echo=TRUE, message=FALSE, warning=FALSE}

q.net <- (grepl("NETWORK ANALYS", io.bdf[, "DE"]) | 
    grepl("NETWORK ANALYS", io.bdf[, "TI"])) & 
	!(grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "DE"]) | 
    grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "TI"]))
q.ena <- grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "DE"]) | 
    grepl("ECOLOGICAL NETWORK ANALYS", io.bdf[, "TI"]) &
    !(q.net)

```

## keyword+title: resilience

```{r mrio-res, echo=TRUE, message=FALSE, warning=FALSE}

q.res <- grepl("^RESILIEN", io.bdf[, "TI"]) | 
    grepl("^RESILIEN", io.bdf[, "DE"]) | 
    grepl(" RESILIEN", io.bdf[, "TI"]) | 
    grepl(" RESILIEN", io.bdf[, "DE"]) 
q.res.abs <- grepl("^RESILIEN", io.bdf[, "TI"]) | 
    grepl("^RESILIEN", io.bdf[, "DE"]) | 
    grepl(" RESILIEN", io.bdf[, "TI"]) | 
    grepl(" RESILIEN", io.bdf[, "DE"]) | 
    grepl("^RESILIEN", io.bdf[, "AB"]) | 
    grepl(" RESILIEN", io.bdf[, "AB"]) 

```

## keyword+title: disturbance(climate change, other)

```{r mrio-dist, echo=TRUE, message=FALSE, warning=FALSE}

q.mc <- grepl("^CLIMATE", io.bdf[, "TI"]) | 
    grepl("^CLIMATE", io.bdf[, "DE"]) | 
    grepl(" CLIMATE", io.bdf[, "TI"]) | 
    grepl(" CLIMATE", io.bdf[, "DE"]) 
q.md <- grepl("^DISTURB", io.bdf[, "TI"]) | 
    grepl("^DISTURB", io.bdf[, "DE"]) | 
    grepl(" DISTURB", io.bdf[, "TI"]) | 
    grepl(" DISTURB", io.bdf[, "DE"]) 

```

## keyword+title: coupled-human natural systems

```{r mrio-chns, echo=TRUE, message=FALSE, warning=FALSE}

q.chns <- grepl("HUMAN-NATURAL", io.bdf[, "TI"]) | 
    grepl("HUMAN-NATURAL", io.bdf[, "DE"]) |
    grepl("HUMAN-NATURAL", io.bdf[, "AB"]) |
    grepl("HUMAN NATURAL", io.bdf[, "TI"]) | 
    grepl("HUMAN NATURAL", io.bdf[, "DE"]) |
    grepl("HUMAN NATURAL", io.bdf[, "AB"]) 

```
## keyword+title: ena & resilience+stability & metrics

```{r mrio-met, echo=TRUE, message=FALSE, warning=FALSE}

q.met <- grepl(" METRIC", io.bdf[, "TI"]) | 
    grepl(" METRIC", io.bdf[, "DE"]) |
    grepl(" METRIC", io.bdf[, "AB"]) |
    grepl("^METRIC", io.bdf[, "TI"]) | 
    grepl("^METRIC", io.bdf[, "DE"]) |
    grepl("^METRIC", io.bdf[, "AB"]) & 
    q.net &
    q.res
q.met.land <- q.met & q.land

```

## type: review 

```{r mrio-rev, echo=TRUE, message=FALSE, warning=FALSE}

q.rev <- grepl("REVIEW", io.bdf[, "DT"]) | 
    grepl("REVIEW", io.bdf[, "DE"]) | 
    grepl("REVIEW", io.bdf[, "TI"]) 
q.ov <- grepl("OVERVIEW", io.bdf[, "DT"]) |
    grepl("OVERVIEW", io.bdf[, "DE"]) | 
    grepl("OVERVIEW", io.bdf[, "TI"]) 

```

# Papers

## QUERY: IO/MRIO

```{r papers-iomrio, echo=TRUE, message=FALSE, warning=FALSE}

head(io.bdf[q.mrio, c("TI")])

```

## QUERY: Reviews/Overviews

```{r papers-rev, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.rev | q.ov, c("TI")]

```

## QUERY: ENA/Network

```{r papers-ena, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.ena | q.ov, c("TI")]

```

```{r papers-net, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.net | q.ov, c("TI")]

```

## QUERY: Metrics

```{r papers-met, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.met, c("TI")]

```

```{r papers-met-land, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.met & q.land, c("TI")]

```


## QUERY: Resilience

```{r papers-res, echo=TRUE, message=FALSE, warning=FALSE}

io.bdf[q.res, c("TI")]

```

# Literature Review: Methods and Background

```{r key-words, echo = TRUE, message = FALSE, warning = FALSE}

kw <- gsub(";", "", unlist(strsplit(io.bdf[q.land, "DE"], split = "; ")))
kw <- sapply(kw, rm.spch)
kw <- unlist(strsplit(kw, " "))
kw.tab <- table(kw)

```

```{R art-year, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=""}

plot(melt(table(io.bdf[, "PY"])), 
	type = "l", xlab = "", ylab = "Articles")

```


```{R kw-treemap, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=""}

data <- melt(kw.tab)
data <- data[order(data[, "value"], decreasing = TRUE), ][1:25, ]
colnames(data) <- c("group", "value")
treemap(data, index=c("group"), vSize="value", type="index",
        fontsize.labels=c(15),
        fontcolor.labels=c("white"),
        fontface.labels=c(2),
        bg.labels=c("transparent"),
        align.labels=list(
            c("center", "center")
        ),
        overlap.labels=0.5,
        inflate.labels=F,
	)

```

```{r query-list, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

q.all <- list("IO_MRIO" = q.mrio, Land = q.land, 
	          "Climate Change" = q.mc, Resilience = q.res,
	          Metric = q.met, Network = q.net, ENA = q.ena, CHNS = q.chns, 
	          "Land Metrics" = q.met.land, Review = (q.rev | q.ov))

```

```{r topic-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}

count <- c(unlist(lapply(q.all, sum)), nrow(io.bdf))
pct <- count / nrow(io.bdf) * 100
pct <- round(pct, 2)
q.df <- data.frame(topic = c(names(q.all), "Total"), count = count, percent = pct)
knitr::kable(q.df, caption = "", booktabs = TRUE, row.names = FALSE)

```


```{r export-query, echo = TRUE, message = FALSE, warning = FALSE}

export_query(io.bdf, q.all, dir = "data/wos-mrio_query", overwrite = TRUE)
mk_review(io.bdf, q.all[-1], file = "results/wos_review.md", overwrite = TRUE)

```

<!-- q.all <- list("IO_MRIO" = q.mrio, Land = q.land, Resilience = q.res, -->
<!-- 	          "Climate Change" = q.mc,  -->
<!-- 	          Metric = q.met, Network = q.net, ENA = q.ena, CHNS = q.chns,  -->
<!-- 	          "Land Metrics" = q.met.land, Review = (q.rev | q.ov)) -->


## Searched and Reviewed "Land" Query

- Searched within queried papers and found papers with MRIO, network
  or resilience
- Need to add telecoupling and land-system science articles
- Recompile using a cross-referencing = LAND & MRIO | NETWORK |
  RESILIENCE | SUSTAINABILITY



# Review

Processing papers compiled in results/wos_review.md

## What reviews are published on the topic of network analysis of landscape extended MRIO?

We found three published reviews/overviews that examine the indirect
effects of consumption on landscapes. The most recent by
@ISI:000435619900021 conducted a global analysis of indirect land
consumption. They found stark disparaties arable land consumption
among countries world-wide. @ISI:000363267800003 conducted a review of
methods for accounting for upstream land-use in traded products and
focusing on two major approaches, accounting based approaches and
environmentally extended input-output analyses, to clarify underlying
conceptual issues with accounting for land-use. The third review by
@ISI:000355026400002 evaluated accounting and evaluation methods used
in calculating land footprints and point to options for further
developing footprint accountting methods, highlighting advantages of
hybridizing different approaches and increasing transparency in
assessments.


### Land

- AN OVERVIEW OF ARABLE LAND USE FOR THE WORLD ECONOMY: FROM SOURCE TO SINK VIA THE GLOBAL SUPPLY CHAIN | WU XD, 2018, LAND USE POL | ISI000435619900021

As an extension of a previous work (Chen and Han, 2015a), this study
explored the arable land use of the world economy from source of
exploitation to sink of final consumption via the global supply chain,
by means of embodiment accounting that includes the indirect feedbacks
associated with both intermediate and primary inputs. In magnitude,
the global transfer of arable land use is estimated to be around 40\%
of the total direct exploitation. The connections as well as
imbalances of major economies in intermediate and final trades of
arable land use are discussed. Canada, Australia, Argentina, Pakistan
and African regions turn out to have a massive deficit of arable land
use in both intermediate and final trades. In contrast, the United
States, Japan, Mainland China, the United Kingdom, Germany and France
obtain a surplus of arable land use in both intermediate and final
trades by land displacement in those net exporters. Indices in terms
of arable land use self-sufficiency rate by source and that by sink
are devised. For India as the biggest source region, around 20\% of
the arable land resources exploited locally are for final consumption
abroad. For the United States as the largest sink region, around 40\%
of its arable land use originates from foreign regions led by
Canada. For Japan as the biggest net importer in both intermediate and
final trades, over 90\% of its arable land use comes from foreign
economies led by African and Asian regions. For sustained development,
regions are suggested to be more adapted to the global supply chain
based on their behaviors in both intermediate and final trades of
arable land use.

- TRADING LAND: A REVIEW OF APPROACHES TO ACCOUNTING FOR UPSTREAM LAND REQUIREMENTS OF TRADED PRODUCTS | SCHAFFARTZIK A, 2015, J IND ECOL | ISI000363267800003

Land use is recognized as a pervasive driver of environmental impacts,
including climate change and biodiversity loss. Global trade leads to
telecoupling between the land use of production and the consumption of
biomass-based goods and services. Telecoupling is captured by accounts
of the upstream land requirements associated with traded products,
also commonly referred to as land footprints. These accounts face
challenges in two main areas: (1) the allocation of land to products
traded and consumed and (2) the metrics to account for differences in
land quality and land-use intensity. For two main families of
accounting approaches (biophysical, factor-based and environmentally
extended input-output analysis), this review discusses conceptual
differences and compares results for land footprints. Biophysical
approaches are able to capture a large number of products and
different land uses, but suffer from a truncation problem. Economic
approaches solve the truncation problem, but are hampered by the
limited disaggregation of sectors and products.  In light of the
conceptual differences, the overall similarity of results generated by
both types of approaches is remarkable.  Diametrically opposed results
for some of the world's largest producers and consumers of
biomass-based products, however, make interpretation difficult. This
review aims to provide clarity on some of the underlying conceptual
issues of accounting for land footprints.

- MEASURING TELECOUPLINGS IN THE GLOBAL LAND SYSTEM: A REVIEW AND COMPARATIVE EVALUATION OF LAND FOOTPRINT ACCOUNTING METHODS | BRUCKNER M, 2015, ECOL ECON | ISI000355026400002

In an increasingly globalized world with more and more distributed
international supply chains, sustainability studies and policies need
to consider socioeconomic and environmental interactions between
distant places. Studies of the global biomass metabolism investigate
physical flows between and within nature and human systems, thus
providing a useful basis for understanding the interrelatedness of
changes in one place with impacts elsewhere. Various methodological
approaches exist for studying the human-nature metabolism and
estimating the land embodied in international trade flows, a core
element of assessing telecouplings in the global land system. The
results of recent studies vary widely, lacking robustness and thus
hampering their application in policy making. This article provides a
structured overview and comparative evaluation of existing accounting
methods and models for calculating land footprints. We identify
differences in available accounting methods and indicate their
shortcomings, which are mainly attributable to the product and supply
chain coverage and detail, and biases introduced by the use of
monetary flows as a proxy for actual physical flows. We suggest
options for further development of global land footprint accounting
methods, particularly highlighting the advantages of hybrid accounting
approaches as a framework for robust and transparent assessments of
the global displacement of land use.


### General consumption
- METABOLISM AND ENVIRONMENTAL IMPACTS OF HOUSEHOLD CONSUMPTION: A REVIEW ON THE ASSESSMENT, METHODOLOGY, AND DRIVERS | DI DONATO M, 2015, J IND ECOL | ISI000363267800019
- ENVIRONMENT IMPACTS OF PRODUCTS - A DETAILED REVIEW OF STUDIES | TUKKER A, 2006, J IND ECOL | ISI000239378800012
- REVIEW OF MODELING TECHNIQUES AND TOOLS FOR DECISION-MAKING IN MANUFACTURING MANAGEMENT | PANDYA KV, 1995, IEE PROC -SCI MEAS TECHNOL | ISIA1995RZ59000006

### Energy consumption
- ENERGY USE IN WORLD ECONOMY FROM HOUSEHOLD-CONSUMPTION-BASED PERSPECTIVE | WU XD, 2019, ENERGY POLICY-a | ISI000463688200028
- NATURAL GAS OVERVIEW FOR WORLD ECONOMY: FROM PRIMARY SUPPLY TO FINAL DEMAND VIA GLOBAL SUPPLY CHAINS | KAN SY, 2019, ENERGY POLICY | ISI000453642600020
- GLOBAL OVERVIEW OF CRUDE OIL USE: FROM SOURCE TO SINK THROUGH INTER-REGIONAL TRADE | WU XF, 2019, ENERGY POLICY | ISI000463688800046

### Carbon footprint
- TOWARDS A UNIVERSAL CARBON FOOTPRINT STANDARD: A CASE STUDY OF CARBON MANAGEMENT AT UNIVERSITIES | ROBINSON OJ, 2018, J CLEAN PROD | ISI000423002500125
- ASSESSING THE URBAN CARBON FOOTPRINT: AN OVERVIEW | LOMBARDI M, 2017, ENVIRON IMPACT ASSESS REV | ISI000410870300005
- HOUSEHOLD CARBON EMISSION RESEARCH: AN ANALYTICAL REVIEW OF MEASUREMENT, INFLUENCING FACTORS AND MITIGATION PROSPECTS | ZHANG X, 2015, J CLEAN PROD | ISI000356990800085
- INPUT-OUTPUT ANALYSIS AND CARBON FOOTPRINTING: AN OVERVIEW OF APPLICATIONS | MINX JC, 2009, ECON SYST RES | ISI000275698000002
- ENERGY AND CO2 LIFE-CYCLE ANALYSES OF WIND TURBINES - REVIEW AND APPLICATIONS | LENZEN M, 2002, RENEW ENERGY | ISI000174693500002

### Water footprint
- GLOBAL SOCIO-HYDROLOGY: AN OVERVIEW OF VIRTUAL WATER USE BY THE WORLD ECONOMY FROM SOURCE OF EXPLOITATION TO SINK OF FINAL CONSUMPTION | WU XD, 2019, J HYDROL | ISI000474327800063

# References
