---
title: "REVIEW: Analysis of the MRIO embodied landscape literature"
author: MK Lau
date: 
output: md_document
fig_caption: yes
bibliography: refs.bib
always_allow_html: yes
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=600)
```

# Overview

## Wed Sep  2 18:14:52 EDT 2020

New project outline

1. Search WOS for MRIO
2. Review articles for ENA and network analysis
3. Review major themes
4. Create a table of metrics

## Wed Sep  9 16:30:03 EDT 2020

*CHEN B, 2018, APPL ENERGY | ISI:000419813100008*

- Energy embodied in trade
- Found small world and scale-free (degree/strength)
- Found 4 regional communities
- Centrality detected USA, China and Germany
- Also evaluated security of energy

*SCHAFFER-SMITH D, 2018, ECOL SOC | ISI:000454653700019*

- Analyzed global soybean trade among countries 1986-2013
- No trade patterns by region
- Link between soybeans and deforestation

*LI Z, 2017, J CLEAN PROD-a | ISI:000407185500007*

- Analyzed trade network structure among sectors for China and Japan
- Centrality analysis showed Japan was dominated by service industries
- China industrial structure is still developing

*TSEKERIS T, 2017, J ECON INTERACT COORD | ISI:000403494800010*

- Analyzed the Greek economy sector trade network
- Used network structure analysis, entrality and clusters
- Integrating value chains could improve efficiency

## Fri Sep  4 14:30:29 EDT 2020

*WANG S, 2018, APPL ENERGY-a | ISI:000445987200037*

- Constructed a energy-water network with China MRIO data
- Conducted IO analysis
- Conducted control analysis

*YANG S, 2016, APPL ENERGY | ISI:000389785200074*

- Assessed the sectoral embodied particular air pollution
- Analyzed using IO and ENA
- Conducted control analysis

*WANG S, 2016, APPL ENERGY | ISI:000382340700062*

- COnstructed an energy water nexus model for Beijing-Tianjin
- Analyzed via IO and control analysis

*ZHANG Y, 2016, J IND ECOL | ISI:000379692600009*

- Constructed a China MRIO for 2002
- Analyzed regional differences

*GUO R, 2016, APPL ENERGY | ISI:000373863500010*

- Water embodied in energy
- IO/ENA

*DU Q, 2018, ENVIRON SCI POLLUT RES | ISI:000441784000087*

- Carbon emission flow network
- Network analysis, including small world, average path length,
  clustering, centrality

*ZHANG Y, 2015, ENERGY POLICY-a | ISI000364246100058*

- Regional energy flow network from 2002 to 2007 in China
- ENA, including integral flow analysis


## Thu Sep  3 16:00:54 EDT 2020

*WANG et al. 2019 J CLEAN PROD-a | ISI:000487237100022*

- Constructed a material flow network model of Tianjian
- Used Control Analysis

*WANG S, 2019, APPL ENERGY | ISI:000454376900064*

- Used China IO sectoral table
- Conducted control analysis


## Wed Sep  2 13:57:50 EDT 2020

*Liang et al. 2020 | ISI:000541775700008*

- Analyzed a global metal flow network from 2009
- Small world network, 2.7 steps to any other department
- 10 communities, highly correlated with economic organizations
- Sector weights are very uneven among networks
- A small number of flows account for 90% of embodied metal
- 78% of trade is within regional economies
- Data: WIOD
- Analyses:
   - small world nature
   - community detection
   - node degree
   - node strength (weighted)
   - centrality (weighted)

*Zhai et al. 2019 | ISI:000470939600041*

- Analyzed urban energy metabolism in Guandong, China via ENA of IO tables
- Used Control and Utility analyses via enaR
- Found various patterns suggesting energy management strategies at
the network scale

ISI:000461262300005 Fang and Chen 2019

- Low quality paper, possibly not peer-reviewed
- AMI/Ascendency analysis of carbon network
- Found a negative correlation between efficiency and redundancy

ISI:000464891000048 Liu et al. 2019

- Analyzed inter-provincial food-related virtual water and land network
- Examined interconnectedness via ENA
- This is one of a series of papers from Saige Wang and colleagues of
embodied energy, water and land mostly using control analysis
- See Research Gate

ISI:000461410100050 Zheng et al. 2019

- ENA and IO analysis of wastewater in Guangdong
- Qunatified direct and indirect wastewater sources and impacts with
  potential strategies for mitigation

See wos_review_tags.md -> %%% You're here mark %%%


## Wed Aug 5 09:28:45 EDT 2020

There has been a substantial amount of work examining embodied
environmental trade via economic and materials trade; however, such
studies focus on integrated metrics that examine inputs and outputs,
i.e. "footprint" and "telecoupling" accounting, and not the structure
of trade network connections. This is possibly both a results of the
origin of the field stemming from economic theory, as well as, data
limitations. The former constraint of theoretical lineage has started
to shift as inter- and trans-disciplinary work has bridged the fields
of economics, ecology and network theory, presenting new opportunities
for synthesis. Also, significant data limitations have been removed as
databases of trade have become available and new models of trade flows
have been constructed from the combination of these data across
temporal, spatial and economic scales. Here, we review the extensive
literature of multi-regional input-output model analysis and examine
the studies that have applied network analysis and theory to the
structure of trade networks. Focusing on environmentally extended
MRIO, we then examine the areas in which significant application of
network analysis is likely to produce interesting and useful insights
for enviromental sustainability and resilience.

After compiling a bibliograhic database of 7803 articles from Web of
Science using the following search of all years from 1900-2020:

TS= ("land-system* science" OR 
"land system* science" OR
telecoupl* OR 
teleconnection OR
"input-output analysis" OR 
"input output analysis" OR 
"multi-regional input-output" OR 
"multiregional input-output" OR 
"multi-regional input output" OR 
"multiregional input output" OR 
"multi regional input-output" OR 
"multi regional input output" OR 
"economic input-output" OR
"economic input output" OR 
"ecological economics")


A search of all titles and keywords in the database for the term
"network analys" excluding the term "eological network analys"
yielded 40 published articles (not invluding books). The search for
the more specific "ecological network analys" yielded 29 studies. 





## Previous Summary

Summary: The goal of this review is to identify the needs for network
analysis of landscape (forests, agriculture, aquatic, built) embodied
in trade to assess the resilience of global human-natural systems to
climate change.

- Why landscape?
  - Major topics in landscape
	- Land-use change
	- Climate change
	- Invasive/disease organisms
	- Fire and drought
   - Resilience and sustainability
- Why MRIO?
  - Multi-regional
  - Multi-industry
- Why networks, why ENA?
  - System-wide impacts through both direct and indirect pathways
  - Feedbacks and cycling
  - Groups and modules
  - ENA is based on IO Analysis framework
  - Compare Approaches (network vs non-network)
	- ENA
	- IO analysis
	- Telecoupling
	- Footprint analysis
	- Other? See Ecol. Econ. 2015 114
	- Virtual systems?
- What has been done?
- What are the priorities?
  - Climate change
  - Land-use change
  - Structural analyses
	- Targets
	- Metrics
  - Coupled Industries
- Comparison of network and non-network metrics


# Analyses

- What work has been done on landscape mrio?
- What work has addressed resilience and stability?
- What ENA metrics have been or could be applied?


## Constructing the Biblio Database

- The Web of Science database was accessed on 11 Aug 2020
- Bib entries with "Topic" matching the following search terms were
  downloaded: TS= ("land-system* science" OR "land system* science" OR
  telecoupl* OR teleconnection OR "input-output analysis" OR "input
  output analysis" OR "multi-regional input-output" OR "multiregional
  input-output" OR "multi-regional input output" OR "multiregional
  input output" OR "multi regional input-output" OR "multi regional
  input output" OR "economic input-output" OR "economic input output"
  OR "ecological economics")
- Entries were further parsed in R using the Bibliometrix package
  using the following workflow (see R/functions.R and R/packages.R) :


```{r drake-plan, eval = FALSE, echo=TRUE, message=FALSE, warning=FALSE}

plan <- drake_plan(
### Load data
    make.refs = mk_refs(),
    io.raw = convert2df("refs.bib", dbsource = "wos", format = "bibtex"),
### Data wrangling
    io.bdf = fix_bdf(io.raw, include.books = FALSE),
    ab.bdf = fix_bdf(io.raw, include.books = TRUE),
### Data checks
    # checks = check_data(io.bdf),
    # check.books = check_data(ab.bdf),
### Analyses
    q.all = mk_q(io.bdf),
    export_query(io.bdf, q.all, dir = "data/wos-mrio_query"),
### Export review spreadsheet
    mk_review(io.bdf, q.all[-1], file = "results/wos_review.md")
### Analytical Checks
### Generate the manuscript
)


```





# Review

Processing papers compiled in results/wos_review.md


## What reviews are published on the topic of network analysis of landscape extended MRIO?

We found three published reviews/overviews that examine the indirect
effects of consumption on landscapes. The most recent by
ISI:000435619900021 conducted a global analysis of indirect land
consumption. They found stark disparaties arable land consumption
among countries world-wide. ISI:000363267800003 conducted a review of
methods for accounting for upstream land-use in traded products and
focusing on two major approaches, accounting based approaches and
environmentally extended input-output analyses, to clarify underlying
conceptual issues with accounting for land-use. The third review by
ISI:000355026400002 evaluated accounting and evaluation methods used
in calculating land footprints and point to options for further
developing footprint accountting methods, highlighting advantages of
hybridizing different approaches and increasing transparency in
assessments.


### Land

- AN OVERVIEW OF ARABLE LAND USE FOR THE WORLD ECONOMY: FROM SOURCE TO
  SINK VIA THE GLOBAL SUPPLY CHAIN | WU XD, 2018, LAND USE POL |
  ISI000435619900021

As an extension of a previous work (Chen and Han, 2015a), this study
explored the arable land use of the world economy from source of
exploitation to sink of final consumption via the global supply chain,
by means of embodiment accounting that includes the indirect feedbacks
associated with both intermediate and primary inputs. In magnitude,
the global transfer of arable land use is estimated to be around 40\%
of the total direct exploitation. The connections as well as
imbalances of major economies in intermediate and final trades of
arable land use are discussed. Canada, Australia, Argentina, Pakistan
and African regions turn out to have a massive deficit of arable land
use in both intermediate and final trades. In contrast, the United
States, Japan, Mainland China, the United Kingdom, Germany and France
obtain a surplus of arable land use in both intermediate and final
trades by land displacement in those net exporters. Indices in terms
of arable land use self-sufficiency rate by source and that by sink
are devised. For India as the biggest source region, around 20\% of
the arable land resources exploited locally are for final consumption
abroad. For the United States as the largest sink region, around 40\%
of its arable land use originates from foreign regions led by
Canada. For Japan as the biggest net importer in both intermediate and
final trades, over 90\% of its arable land use comes from foreign
economies led by African and Asian regions. For sustained development,
regions are suggested to be more adapted to the global supply chain
based on their behaviors in both intermediate and final trades of
arable land use.

- TRADING LAND: A REVIEW OF APPROACHES TO ACCOUNTING FOR UPSTREAM LAND
  REQUIREMENTS OF TRADED PRODUCTS | SCHAFFARTZIK A, 2015, J IND ECOL |
  ISI000363267800003

Land use is recognized as a pervasive driver of environmental impacts,
including climate change and biodiversity loss. Global trade leads to
telecoupling between the land use of production and the consumption of
biomass-based goods and services. Telecoupling is captured by accounts
of the upstream land requirements associated with traded products,
also commonly referred to as land footprints. These accounts face
challenges in two main areas: (1) the allocation of land to products
traded and consumed and (2) the metrics to account for differences in
land quality and land-use intensity. For two main families of
accounting approaches (biophysical, factor-based and environmentally
extended input-output analysis), this review discusses conceptual
differences and compares results for land footprints. Biophysical
approaches are able to capture a large number of products and
different land uses, but suffer from a truncation problem. Economic
approaches solve the truncation problem, but are hampered by the
limited disaggregation of sectors and products.  In light of the
conceptual differences, the overall similarity of results generated by
both types of approaches is remarkable.  Diametrically opposed results
for some of the world's largest producers and consumers of
biomass-based products, however, make interpretation difficult. This
review aims to provide clarity on some of the underlying conceptual
issues of accounting for land footprints.

- MEASURING TELECOUPLINGS IN THE GLOBAL LAND SYSTEM: A REVIEW AND
  COMPARATIVE EVALUATION OF LAND FOOTPRINT ACCOUNTING METHODS |
  BRUCKNER M, 2015, ECOL ECON | ISI000355026400002

In an increasingly globalized world with more and more distributed
international supply chains, sustainability studies and policies need
to consider socioeconomic and environmental interactions between
distant places. Studies of the global biomass metabolism investigate
physical flows between and within nature and human systems, thus
providing a useful basis for understanding the interrelatedness of
changes in one place with impacts elsewhere. Various methodological
approaches exist for studying the human-nature metabolism and
estimating the land embodied in international trade flows, a core
element of assessing telecouplings in the global land system. The
results of recent studies vary widely, lacking robustness and thus
hampering their application in policy making. This article provides a
structured overview and comparative evaluation of existing accounting
methods and models for calculating land footprints. We identify
differences in available accounting methods and indicate their
shortcomings, which are mainly attributable to the product and supply
chain coverage and detail, and biases introduced by the use of
monetary flows as a proxy for actual physical flows. We suggest
options for further development of global land footprint accounting
methods, particularly highlighting the advantages of hybrid accounting
approaches as a framework for robust and transparent assessments of
the global displacement of land use.


### General consumption
- METABOLISM AND ENVIRONMENTAL IMPACTS OF HOUSEHOLD CONSUMPTION: A
  REVIEW ON THE ASSESSMENT, METHODOLOGY, AND DRIVERS | DI DONATO M,
  2015, J IND ECOL | ISI000363267800019
- ENVIRONMENT IMPACTS OF PRODUCTS - A DETAILED REVIEW OF STUDIES |
  TUKKER A, 2006, J IND ECOL | ISI000239378800012
- REVIEW OF MODELING TECHNIQUES AND TOOLS FOR DECISION-MAKING IN
  MANUFACTURING MANAGEMENT | PANDYA KV, 1995, IEE PROC -SCI MEAS
  TECHNOL | ISIA1995RZ59000006

### Energy consumption
- ENERGY USE IN WORLD ECONOMY FROM HOUSEHOLD-CONSUMPTION-BASED PERSPECTIVE | WU XD, 2019, ENERGY POLICY-a | ISI000463688200028
- NATURAL GAS OVERVIEW FOR WORLD ECONOMY: FROM PRIMARY SUPPLY TO FINAL DEMAND VIA GLOBAL SUPPLY CHAINS | KAN SY, 2019, ENERGY POLICY | ISI000453642600020
- GLOBAL OVERVIEW OF CRUDE OIL USE: FROM SOURCE TO SINK THROUGH INTER-REGIONAL TRADE | WU XF, 2019, ENERGY POLICY | ISI000463688800046

### Carbon footprint
- TOWARDS A UNIVERSAL CARBON FOOTPRINT STANDARD: A CASE STUDY OF CARBON MANAGEMENT AT UNIVERSITIES | ROBINSON OJ, 2018, J CLEAN PROD | ISI000423002500125
- ASSESSING THE URBAN CARBON FOOTPRINT: AN OVERVIEW | LOMBARDI M, 2017, ENVIRON IMPACT ASSESS REV | ISI000410870300005
- HOUSEHOLD CARBON EMISSION RESEARCH: AN ANALYTICAL REVIEW OF MEASUREMENT, INFLUENCING FACTORS AND MITIGATION PROSPECTS | ZHANG X, 2015, J CLEAN PROD | ISI000356990800085
- INPUT-OUTPUT ANALYSIS AND CARBON FOOTPRINTING: AN OVERVIEW OF APPLICATIONS | MINX JC, 2009, ECON SYST RES | ISI000275698000002
- ENERGY AND CO2 LIFE-CYCLE ANALYSES OF WIND TURBINES - REVIEW AND APPLICATIONS | LENZEN M, 2002, RENEW ENERGY | ISI000174693500002

### Water footprint
- GLOBAL SOCIO-HYDROLOGY: AN OVERVIEW OF VIRTUAL WATER USE BY THE WORLD ECONOMY FROM SOURCE OF EXPLOITATION TO SINK OF FINAL CONSUMPTION | WU XD, 2019, J HYDROL | ISI000474327800063


## How does IO analysis differ from ENA/network analysis?

Someone must have already published this:

- NETWORK ANALYSIS APPLIED TO LARGE-SCALE CYBER-ECOSYSTEMS | FATH BD,
  2004, ECOL MODEL | ISI000188994300001

Develops cyber models.

- THEORY OF MATERIALS AND ENERGY FLOW ANALYSIS IN ECOLOGY AND
  ECONOMICS | SUH S, 2005, ECOL MODEL | ISI000233798200002

This is a good mathematical overview of ENA metrics.

- REVIEW OF THE FOUNDATIONS OF NETWORK ENVIRON ANALYSIS | FATH

This is another good review.

- ENERGY WATER NEXUS UNDER ENERGY MIX SCENARIOS USING INPUT OUTPUT AND
  ECOLOGICAL NETWORK ANALYSES | WANG S, 2019, APPL ENERGY |
  ISI000454376900064

- INFORMATION-BASED ECOLOGICAL NETWORK ANALYSIS FOR CARBON EMISSIONS |
  FANG D, 2019, APPL ENERGY | ISI000461262300005

- NETWORK ANALYSIS AS A TOOL FOR QUANTIFYING THE DYNAMICS OF
  METACOUPLED SYSTEMS: AN EXAMPLE USING GLOBAL SOYBEAN TRADE |
  SCHAFFER-SMITH D, 2018, ECOL SOC | ISI000454653700019

- A NETWORK ANALYSIS OF INDIRECT CARBON EMISSION FLOWS AMONG DIFFERENT
  INDUSTRIES IN CHINA | DU Q, 2018, ENVIRON SCI POLLUT RES |
  ISI000441784000087

- EVOLUTION OF THE SCIENTIFIC LITERATURE ON INPUT-OUTPUT ANALYSIS: A
  BIBLIOMETRIC ANALYSIS OF 1990-2017 | XIE Y, 2018, SUSTAINABILITY |
  ISI000446770200178

- MULTI-REGIONAL INPUT-OUTPUT MODEL AND ECOLOGICAL NETWORK ANALYSIS
  FOR REGIONAL EMBODIED ENERGY ACCOUNTING IN CHINA | ZHANG Y, 2015,
  ENERGY POLICY-a | ISI000364246100058

- ECOLOGICAL NETWORK ANALYSIS OF AN URBAN METABOLIC SYSTEM BASED ON
  INPUT-OUTPUT TABLES: MODEL DEVELOPMENT AND CASE STUDY FOR BEIJING |
  ZHANG Y, 2014, SCI TOTAL ENVIRON | ISI000331776000069


## What are the studies applying ENA to MRIO?
### ENA/MRIO

- UNFOLDING INTERREGIONAL ENERGY FLOW STRUCTURE OF CHINA'S
  CONSTRUCTION SECTOR BASED ON PROVINCE-LEVEL DATA | WEN Q, 2020, J
  ENVIRON MANAGE | ISI000501617600023
- EVALUATING CHROMIUM COUPLED WITH CARBON METABOLISM AND ENVIRONMENTAL
  PERFORMANCE IN THE CHROMATE INDUSTRIAL SYMBIOSIS NETWORK IN CHINA |
  WU JUNNIAN WJ, 2019, RESOUR CONSERV RECYCL | ISI000483414300019
- ECOLOGICAL NETWORK ANALYSIS OF AN ENERGY METABOLISM SYSTEM BASED ON
  INPUT-OUTPUT TABLES: MODEL DEVELOPMENT AND CASE STUDY FOR GUANGDONG
  | ZHAI M, 2019, J CLEAN PROD | ISI000470939600041
- CHARACTERIZING THE EMBODIED CARBON EMISSIONS FLOWS AND ECOLOGICAL
  RELATIONSHIPS AMONG FOUR CHINESE MEGACITIES AND OTHER PROVINCES |
  WANG X, 2019, SUSTAINABILITY | ISI000469518700139
- METABOLISM OF URBAN WASTEWATER: ECOLOGICAL NETWORK ANALYSIS FOR
  GUANGDONG PROVINCE, CHINA | ZHENG B, 2019, J CLEAN PROD |
  ISI000461410100050
- INFORMATION-BASED ECOLOGICAL NETWORK ANALYSIS FOR CARBON EMISSIONS |
  FANG D, 2019, APPL ENERGY | ISI000461262300005
- WATER-LAND NEXUS IN FOOD TRADE BASED ON ECOLOGICAL NETWORK ANALYSIS
  | LIU Y, 2019, ECOL INDIC | ISI000464891000048
- ENERGY WATER NEXUS UNDER ENERGY MIX SCENARIOS USING INPUT OUTPUT AND
  ECOLOGICAL NETWORK ANALYSES | WANG S, 2019, APPL ENERGY |
  ISI000454376900064
- ECOLOGICAL NETWORK ANALYSIS FOR AN INDUSTRIAL SOLID WASTE METABOLISM
  SYSTEM | GUAN Y, 2019, ENVIRON POLLUT | ISI000452940700031
- CHARACTERISTICS OF TIANJIN'S MATERIAL METABOLISM FROM THE
  PERSPECTIVE OF ECOLOGICAL NETWORK ANALYSIS | WANG X, 2019, J CLEAN
  PROD-a | ISI000487237100022
- AN ECOLOGICAL-THERMODYNAMIC APPROACH TO URBAN METABOLISM: MEASURING
  RESOURCE UTILIZATION WITH OPEN SYSTEM NETWORK EFFECTIVENESS ANALYSIS
  | TAN LM, 2019, APPL ENERGY | ISI000497974600026
- ECOLOGICAL AND ECONOMIC ANALYSES OF THE FOREST METABOLISM SYSTEM: A
  CASE STUDY OF GUANGDONG PROVINCE, CHINA | ZHANG X, 2018, ECOL INDIC
  | ISI000456907400014
- ECOLOGICAL NETWORK ANALYSIS ON INTRA-CITY METABOLISM OF FUNCTIONAL
  URBAN AREAS IN ENGLAND AND WALES | TAN LM, 2018, RESOUR CONSERV
  RECYCL | ISI000444789400017
- INTERREGIONAL CARBON FLOWS OF CHINA | DUAN C, 2018, APPL ENERGY |
  ISI000445987200036
- MULTIREGIONAL INPUT-OUTPUT AND ECOLOGICAL NETWORK ANALYSES FOR
  REGIONAL ENERGY-WATER NEXUS WITHIN CHINA | WANG S, 2018, APPL
  ENERGY-a | ISI000445987200037
- PROVINCIAL CARBON EMISSIONS REDUCTION ALLOCATION PLAN IN CHINA BASED
  ON CONSUMPTION PERSPECTIVE | WANG X, 2018, SUSTAINABILITY |
  ISI000435587100038
- INTERREGIONAL TRADE AMONG REGIONS OF URBAN ENERGY METABOLISM: A CASE
  STUDY BETWEEN BEIJING-TIANJIN-HEBEI AND OTHERS IN CHINA | ZHENG H,
  2018, RESOUR CONSERV RECYCL | ISI000428828300034
- MULTI-SCALE ANALYSIS OF THE ENERGY METABOLIC PROCESSES IN THE
  BEIJING-TIANJIN-HEBEI (JING-JIN-JI) URBAN AGGLOMERATION | HAO Y,
  2018, ECOL MODEL | ISI000425078000004
- ECOLOGICAL UTILITY THEORY: SOLVING A SERIES CONVERGENCE ISSUE |
  KAZANCI C, 2017, ECOL MODEL | ISI000405046800003
- ENERGY-WATER NEXUS OF INTERNATIONAL ENERGY TRADE OF CHINA | DUAN C,
  2017, APPL ENERGY | ISI000399623600067
- ECOLOGICAL NETWORK ANALYSIS OF ENERGY METABOLISM IN THE
  BEIJING-TIANJIN-HEBEI (JING-JIN-JI) URBAN AGGLOMERATION | ZHANG Y,
  2017, ECOL MODEL | ISI000399259300005
- HIGHLY VARIABLE MALE COURTSHIP BEHAVIORAL SEQUENCES IN A CRAMBID
  MOTH | FARRELL SL, 2017, J ETHOL | ISI000400078900009
- ECOLOGICAL NETWORK ANALYSIS OF EMBODIED PARTICULATE MATTER 2.5-A
  CASE STUDY OF BEIJING | YANG S, 2016, APPL ENERGY |
  ISI000389785200074
- SIX GENERAL ECOSYSTEM PROPERTIES ARE MORE INTENSE IN BIOGEOCHEMICAL
  CYCLING NETWORKS THAN FOOD WEBS | BORRETT SR, 2016, J COMPLEX NETW |
  ISI000447240800006
- ENERGY-WATER NEXUS OF URBAN AGGLOMERATION BASED ON MULTIREGIONAL
  INPUT-OUTPUT TABLES AND ECOLOGICAL NETWORK ANALYSIS: A CASE STUDY OF
  THE BEIJING-TIANJIN-HEBEI REGION | WANG S, 2016, APPL ENERGY |
  ISI000382340700062
- ECOLOGICAL NETWORK ANALYSIS OF EMBODIED ENERGY EXCHANGES AMONG THE
  SEVEN REGIONS OF CHINA | ZHANG Y, 2016, J IND ECOL |
  ISI000379692600009
- ECOLOGICAL NETWORK ANALYSIS OF THE VIRTUAL WATER NETWORK WITHIN
  CHINA'S ELECTRIC POWER SYSTEM DURING 2007-2012 | GUO R, 2016, APPL
  ENERGY | ISI000373863500010
- URBAN ENERGY FLOW PROCESSES IN THE BEIJING-TIANJIN-HEBEI
  (JING-JIN-JI) URBAN AGGLOMERATION: COMBINING MULTI-REGIONAL
  INPUT-OUTPUT TABLES WITH ECOLOGICAL NETWORK ANALYSIS | ZHANG Y,
  2016, J CLEAN PROD | ISI000384626400024
- MULTI-REGIONAL INPUT-OUTPUT MODEL AND ECOLOGICAL NETWORK ANALYSIS
  FOR REGIONAL EMBODIED ENERGY ACCOUNTING IN CHINA | ZHANG Y, 2015,
  ENERGY POLICY-a | ISI000364246100058
- URBAN ENERGY CONSUMPTION: DIFFERENT INSIGHTS FROM ENERGY FLOW
  ANALYSIS, INPUT-OUTPUT ANALYSIS AND ECOLOGICAL NETWORK ANALYSIS |
  CHEN S, 2015, APPL ENERGY | ISI000347582700009
- ECOLOGICAL NETWORK ANALYSIS OF AN URBAN METABOLIC SYSTEM BASED ON
  INPUT-OUTPUT TABLES: MODEL DEVELOPMENT AND CASE STUDY FOR BEIJING |
  ZHANG Y, 2014, SCI TOTAL ENVIRON | ISI000331776000069
- THROUGHFLOW CENTRALITY IS A GLOBAL INDICATOR OF THE FUNCTIONAL
  IMPORTANCE OF SPECIES IN ECOSYSTEMS | BORRETT SR, 2013, ECOL INDIC |
  ISI000319891900022
- IMPROVED ECOLOGICAL NETWORK ANALYSIS FOR ENVIRONMENTAL
  SUSTAINABILITY ASSESSMENT; A CASE STUDY ON A FOREST ECOSYSTEM |
  SCHAUBROECK T, 2012, ECOL MODEL | ISI000313089600015
- EQUIVALENCE OF THE REALIZED INPUT AND OUTPUT ORIENTED INDIRECT
  EFFECTS METRICS IN ECOLOGICAL NETWORK ANALYSIS | BORRETT SR, 2011,
  ECOL MODEL-a | ISI000292581400011
- A MATLAB (R) FUNCTION FOR NETWORK ENVIRON ANALYSIS | FATH BD, 2006,
  ENVIRON MODELL SOFTW | ISI000236049400007

### Network/MRIO

- CARBON NETWORK EMBODIED IN INTERNATIONAL TRADE: GLOBAL STRUCTURAL
  EVOLUTION AND ITS POLICY IMPLICATIONS | LI YL, 2020, ENERGY POLICY |
  ISI000528255000027
- LINKING AGRICULTURAL GHG EMISSIONS TO GLOBAL TRADE NETWORK | ZHAO X,
  2020, EARTH FUTURE | ISI000522205300004
- EVOLUTION OF VIRTUAL WATER METABOLIC NETWORK IN DEVELOPING REGIONS:
  A CASE STUDY OF GUANGDONG PROVINCE | HE C, 2020, ECOL INDIC |
  ISI000493902400069
- CARBON COMMUNITIES AND HOTSPOTS FOR CARBON EMISSIONS REDUCTION IN
  CHINA | HUANG L, 2019, SUSTAINABILITY | ISI000493525500367
- ENERGY FOOTPRINT PATHWAYS OF CHINA | TIAN X, 2019, ENERGY |
  ISI000474315800026
- A STUDY ON EMBODIED CARBON TRANSFER AT THE PROVINCIAL LEVEL OF CHINA
  FROM A SOCIAL NETWORK PERSPECTIVE | LV K, 2019, J CLEAN PROD |
  ISI000468709400089
- LINKAGE ANALYSIS OF TOURISM-RELATED SECTORS IN CHINA: AN ASSESSMENT
  BASED ON NETWORK ANALYSIS TECHNIQUE | ZHA J, 2019, INT J TOUR RES |
  ISI000474282600010
- ENERGY-INDUCED MERCURY EMISSIONS IN GLOBAL SUPPLY CHAIN NETWORKS:
  STRUCTURAL CHARACTERISTICS AND POLICY IMPLICATIONS | CHEN B, 2019,
  SCI TOTAL ENVIRON | ISI000464681800010
- NETWORK ANALYSIS OF DIFFERENT TYPES OF FOOD FLOWS: ESTABLISHING THE
  INTERACTION BETWEEN FOOD FLOWS AND ECONOMIC FLOWS | ZHAI M, 2019,
  RESOUR CONSERV RECYCL | ISI000458222600016
- LAND COMPETITION UNDER TELECOUPLING: DISTANT ACTORS' ENVIRONMENTAL
  VERSUS ECONOMIC CLAIMS ON LAND IN NORTH-EASTERN MADAGASCAR |
  ANDRIAMIHAJA OR, 2019, SUSTAINABILITY | ISI000458929500296
- DYNAMIC INPUT-OUTPUT ANALYSIS FOR ENERGY METABOLISM SYSTEM IN THE
  PROVINCE OF GUANGDONG, CHINA | ZHAI M, 2018, J CLEAN PROD |
  ISI000444364400065
- EVOLUTION OF THE SCIENTIFIC LITERATURE ON INPUT-OUTPUT ANALYSIS: A
  BIBLIOMETRIC ANALYSIS OF 1990-2017 | XIE Y, 2018, SUSTAINABILITY |
  ISI000446770200178
- VISUALIZING THE CHANGE OF EMBODIED CO2 EMISSIONS ALONG GLOBAL
  PRODUCTION CHAINS | DUAN Y, 2018, J CLEAN PROD | ISI000438003200045
- A NETWORK ANALYSIS OF INDIRECT CARBON EMISSION FLOWS AMONG DIFFERENT
  INDUSTRIES IN CHINA | DU Q, 2018, ENVIRON SCI POLLUT RES |
  ISI000441784000087
- SYSTEMIC RISK IN THE GLOBAL WATER INPUT-OUTPUT NETWORK | DISTEFANO
  T, 2018, WATER RESOUR ECON | ISI000440380800003
- INDUSTRIAL CHARACTERISTICS AND CONSUMPTION EFFICIENCY FROM A NEXUS
  PERSPECTIVE - BASED ON ANHUI'S EMPIRICAL STATISTICS | CHEN Z, 2018,
  ENERGY POLICY | ISI000428099800029
- AN INQUIRY INTO WATER TRANSFER NETWORK OF THE YANGTZE RIVER ECONOMIC
  BELT IN CHINA | TAN F, 2018, J CLEAN PROD | ISI000423648000027
- EMERGY NETWORK ANALYSIS OF CHINESE SECTORAL ECOLOGICAL
  SUSTAINABILITY | SUN X, 2018, J CLEAN PROD | ISI000424727100050
- GLOBAL ENERGY FLOWS EMBODIED IN INTERNATIONAL TRADE: A COMBINATION
  OF ENVIRONMENTALLY EXTENDED INPUT-OUTPUT ANALYSIS AND COMPLEX
  NETWORK ANALYSIS | CHEN B, 2018, APPL ENERGY | ISI000419813100008
- NETWORK ANALYSIS AS A TOOL FOR QUANTIFYING THE DYNAMICS OF
  METACOUPLED SYSTEMS: AN EXAMPLE USING GLOBAL SOYBEAN TRADE |
  SCHAFFER-SMITH D, 2018, ECOL SOC | ISI000454653700019
- FLOWBCA: A FLOW-BASED CLUSTER ALGORITHM IN STATA | MEEKES J, 2018,
  STATA J | ISI000445991000005
- EXAMINING INDUSTRIAL STRUCTURE CHANGES AND CORRESPONDING CARBON
  EMISSION REDUCTION EFFECT BY COMBINING INPUT-OUTPUT ANALYSIS AND
  SOCIAL NETWORK ANALYSIS: A COMPARISON STUDY OF CHINA AND JAPAN | LI
  Z, 2017, J CLEAN PROD-a | ISI000407185500007
- IDENTIFY SECTORS' ROLE ON THE EMBEDDED CO2 TRANSFER NETWORKS THROUGH
  CHINA'S REGIONAL TRADE | WANG Z, 2017, ECOL INDIC |
  ISI000406436100012
- NETWORK ANALYSIS OF INTER-SECTORAL RELATIONSHIPS AND KEY SECTORS IN
  THE GREEK ECONOMY | TSEKERIS T, 2017, J ECON INTERACT COORD |
  ISI000403494800010
- AN URBAN METABOLISM AND CARBON FOOTPRINT ANALYSIS OF THE JING-JIN-JI
  REGIONAL AGGLOMERATION | ZHENG H, 2017, J IND ECOL |
  ISI000397410600013
- AUSTRALIA'S REGIONAL INNOVATION SYSTEMS: INTER-INDUSTRY INTERACTION
  IN INNOVATIVE ACTIVITIES IN THREE AUSTRALIAN TERRITORIES | SCHUETZ
  MH, 2017, ECON SYST RES | ISI000405565200003
- URBAN ENERGY-WATER NEXUS: A NETWORK PERSPECTIVE | CHEN S, 2016, APPL
  ENERGY | ISI000389785200076
- UNEQUAL CARBON EXCHANGES THE ENVIRONMENTAL AND ECONOMIC IMPACTS OF
  ICONIC US CONSUMPTION ITEMS | PRELL C, 2016, J IND ECOL |
  ISI000379692600015
- WEALTH AND POLLUTION INEQUALITIES OF GLOBAL TRADE: A NETWORK AND
  INPUT-OUTPUT APPROACH | PRELL C, 2016, SOC SCI J |
  ISI000371797100013
- ANALYSIS OF URBAN ENERGY CONSUMPTION IN CARBON METABOLIC PROCESSES
  AND ITS STRUCTURAL ATTRIBUTES: A CASE STUDY FOR BEIJING | ZHANG Y,
  2015, J CLEAN PROD | ISI000356990800086
- ENAR: ANR PACKAGE FOR ECOSYSTEM NETWORK ANALYSIS | BORRETT SR, 2014,
  METHODS ECOL EVOL | ISI000345762000009
- ECOSYSTEM NETWORK ANALYSIS INDICATORS ARE GENERALLY ROBUST TO
  PARAMETER UNCERTAINTY IN A PHOSPHORUS MODEL OF LAKE SIDNEY LANIER,
  USA | KAUFMAN AG, 2010, ECOL MODEL | ISI000276574900015
- APPLYING SOCIAL NETWORK ANALYSIS TO INPUT-OUTPUT BASED INNOVATION
  MATRICES: AN ILLUSTRATIVE APPLICATION TO SIX OECD TECHNOLOGICAL
  SYSTEMS FOR THE MIDDLE 1990S | MONTRESOR S, 2009, ECON SYST RES |
  ISI000273938700003
- LEAST-INFERENCE METHODS FOR CONSTRUCTING NETWORKS OF TROPHIC FLOWS |
  ULANOWICZ RE, 2008, ECOL MODEL | ISI000252654800007
- CREATING AN ACADEMIC LANDSCAPE OF SUSTAINABILITY SCIENCE: AN
  ANALYSIS OF THE CITATION NETWORK | KAJIKAWA Y, 2007, SUSTAIN SCI |
  ISI000206302000007
- THEORY OF MATERIALS AND ENERGY FLOW ANALYSIS IN ECOLOGY AND
  ECONOMICS | SUH S, 2005, ECOL MODEL | ISI000233798200002
- NETWORK ANALYSIS APPLIED TO LARGE-SCALE CYBER-ECOSYSTEMS | FATH BD,
  2004, ECOL MODEL | ISI000188994300001
- NETWORK SYNERGISM: EMERGENCE OF POSITIVE RELATIONS IN ECOLOGICAL
  SYSTEMS | FATH BD, 1998, ECOL MODEL | ISI000073521200003
- CARBON BUDGET AND NETWORK ANALYSIS OF A HIGH-ENERGY BEACH/SURF-ZONE
  ECOSYSTEM | HEYMANS JJ, 1996, ESTUAR COAST SHELF SCI |
  ISIA1996VL79800006


### What studies are there of landscapes?
### Only three papers explicitely applying ENA to forests

- ECOLOGICAL AND ECONOMIC ANALYSES OF THE FOREST METABOLISM SYSTEM: A
  CASE STUDY OF GUANGDONG PROVINCE, CHINA | ZHANG X, 2018, ECOL INDIC
  | ISI000456907400014
- AN INQUIRY INTO WATER TRANSFER NETWORK OF THE YANGTZE RIVER ECONOMIC
  BELT IN CHINA | TAN F, 2018, J CLEAN PROD | ISI000423648000027
- IMPROVED ECOLOGICAL NETWORK ANALYSIS FOR ENVIRONMENTAL
  SUSTAINABILITY ASSESSMENT; A CASE STUDY ON A FOREST ECOSYSTEM |
  SCHAUBROECK T, 2012, ECOL MODEL | ISI000313089600015



# References
