---
title: "REVIEW: Analysis of the MRIO embodied landscape literature"
author: MK Lau
date: 
output: md_document
fig_caption: yes
bibliography: refs.bib
always_allow_html: yes

# Latex settings
header-includes:
  - \usepackage{endfloat}
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=600)
```

- What work has been done on landscape mrio?
- What work has addressed resilience and stability?
- What ENA metrics have been or could be applied?

# Analyses

- keyword+title: mrio & landscape
- keyword+title: mrio & ena
- keyword+title: " & resilience+stability
- keyword+title: mrio & disturbance(climate change, other)
- keyword+title: coupled-human natural systems
- keyword+title: ena & resilience+stability & metrics





```{r figRef, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure caption here"}
plot(1:5)

```

\@ref(fig:figRef) 


```{r tabRef, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
# data(iris)
# df <- head(iris)
# knitr::kable(df, caption = "Table caption here...", booktabs = TRUE)
```

\@ref(tab:tabRef)


# References
